### 2011-09-21 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: In progress.

According to \cite{Mlynkova:2008:AAX:1494650.1495496} The type of the inference method can be divided into \emph{heuristic} and \emph{grammar-inferring}. Heuristic methods are based on experience with manual construction of schemas and their result commonly does not belong to any class of grammar. On the contrary, result of the grammar-inferring methods belongs to a particular class of languages with specific characteristics.

Another important criterion is the type of input data. Most of the approaches process XML documents as the input of the inference process and the documents are supposed to be valid against the resulting schema. Besides approaches exploiting XML data, approaches that utilize operations over XML data may be developed and they are the most significant approaches in terms of this work.

According to our best knowledge at the time of writing there is just one approach of this category. It utilizes a set of XQuery queries to discover keys and foreign keys\todo{ref do literatury? Ty by tady něškodily všude, u každé té kategorie.}.

@@

\section{Approaches that Utilize XML Documents}
The process of inference commonly used by a significant number of approaches is summarized in \cite{Mlynkova:2008:AAX:1494650.1495496} as the following one: For each occurrence of element $e$ from the input XML documents and its subelements $e_1, e_2, ..., e_k$ a production $e \rightarrow e_1 e_2 ... e_k$ is constructed. The productions form so-called \emph{initial grammar} (IG). For each element type the productions are then merged, simplified and generalized using various methods and criteria. A common approach is so-called \emph{merging state algorithm}, where a \emph{prefix tree automaton} (PTA) is built from the productions of the same element type and the automaton is generalized via merging of its states. Finally, the generalized automaton/grammar is expressed in syntax of the respective XML schema language.

\todo[inline]{Tady by neškodilo dát odkazy na všechny ex. přístupy a říct, že popíšeme detailněji aspoň dva.}

\subsection{XTRACT}
The XTRACT \todo{bibref} system is an example of a \emph{heuristic} \emph{merging state algorithm} creating the result in DTD. Its process of inference consists of three steps:
\begin{enumerate}
\item Generalization - Generates a set of DTD candidates by searching the input for certain patterns and generalising corresponding fragments using regular expressions.
\item Factoring - Groups of generalized candidate DTDs are factorized to a new ones by finding common sub-expressions to make them more concise. \todo[inline]{priklad}
\item Minimum Description Length (MDL) Principle - Composing a near-optimal DTD schema from the set of all generalized candidate DTDs.
\end{enumerate}

MDL is the most important step. It ranks each DTD candidate using two aspects - conciseness and preciseness. Conciseness of a DTD is expressed by using the number of bits required to describe the DTD (the smaller, the better). Preciseness of a DTD is expressed using the number of bits required for description of the input data using the DTD. In other words, the more accurately the structure is described, the fewer bits are required. Since the two conditions are contradictory, their balancing brings reasonable and realistic results.

\subsection{SchemaMiner}
The SchemaMiner system \todo{bibref} is another example of a \emph{heuristic} \emph{merging state algorithm} creating the result in XSD. It focuses on inferring elements with the same name but different structure and unordered sequences.is another example of a \emph{heuristic} \emph{merging state algorithm} creating the result in XSD. It focuses on inferring elements with the same name but different structure and unordered sequences.
\todo[inline]{Definovat skratku XSD a co to je element type.}

@@

\begin{itemize}
\renewcommand{\theenumi}{(O\arabic{enumi})}
\renewcommand{\labelenumi}{\theenumi}
\item $L_1$ is a key of the elements $S_1$, $L_2$ is a respective foreign key and it itself is not a key of the elements $S_2$.
\item $L_2$ is a key of the elements $S_2$, $L_1$ is a respective foreign key and it cannot be decided whether $L_1$ is a key of the elements $S_1$ or not.
\end{itemize}

@@

The pattern occurrence is considered of case (O1) if it is the for join pattern (weight: 1), aggregation function \texttt{avg}, \texttt{min}, \texttt{max} or \texttt{sum} is applied on a return path (weight: 1), aggregation function \texttt{count} is applied on a return path. \todo {definovat return path?}

>>>>

According to \cite{Mlynkova:2008:AAX:1494650.1495496}, the type of the inference method can be divided into \emph{heuristic} and \emph{grammar-inferring}. Heuristic methods are based on experience with manual construction of schemas, motivated by real-life usages of XML schemata, and their result commonly does not belong to any class of grammar. On the contrary, the grammar-inferring methods are based on theoretical knowledge of automata and their results belong to a particular class of languages. Thus, these methods guarantee specific characteristics of the results. \todo[inline]{Tady by neškodilo dát odkazy na všechny ex. přístupy a říct, že popíšeme detailněji aspoň dva.}

Another important criterion is the type of input data. Most of the approaches process XML documents as the input of the inference process and the documents are supposed to be valid against the resulting schema. Besides approaches exploiting XML data, approaches that utilize other or additional sources may be developed. An approach utilizing XML data along with an obsolete XML schema is described in \cite{Mlynkova:2009:IXS:1862681.1862693}. However, the most significant approaches in terms of this work are those, utilizing operations over XML data. According to our best knowledge at the time of writing, there is just one approach of this category, described in \cite{Necasky:2009:DXK:1529282.1529414}. It utilizes a set of XQuery queries to discover keys and foreign keys\todo{ref do literatury - Ty by tady něškodily všude, u každé té kategorie.}.

\section{Common Caracteristics}
The process of inference commonly used by a significant number of approaches is summarized in \cite{Mlynkova:2008:AAX:1494650.1495496} as the following one: For each occurrence of element $e$ from the input XML documents and its subelements $e_1, e_2, ..., e_k$ a production $e \rightarrow e_1 e_2 ... e_k$ is constructed. The productions form so-called \emph{initial grammar} (IG). For each element type the productions are then merged, simplified and generalized using various methods and criteria. A common approach is so-called \emph{merging state algorithm}, where a \emph{prefix tree automaton} (PTA) is built from the productions of the same element type and the automaton is generalized via merging of its states. Finally, the generalized automaton/grammar is expressed in syntax of the respective XML schema language.
\todo[inline]{Tento odstavec je doslovne prebraty z uvedeneho clanku. Mozem to takto pouzit?}

\section{XTRACT}
The XTRACT \cite{Garofalakis:2000:XSE:342009.335409} system is an example of a \emph{heuristic} \emph{merging state algorithm} creating the result in DTD. Its process of inference consists of three steps:
\begin{enumerate}
\item Generalization - Generates a set of DTD candidates by searching the input for certain patterns and generalising corresponding fragments using regular expressions.
\item Factoring - Groups of generalized candidate DTDs are factorized to a new ones by finding common sub-expressions to make them more concise.
\item Minimum Description Length (MDL) Principle - Composing a near-optimal DTD schema from the set of all generalized candidate DTDs.
\end{enumerate}

\subsection{Generalization}
Purpose of generalization is to create a set of DTD candidates - schemata that cover fractions of the input XML data. In the last step, this set will be used to compose a (sub)optimal result with respect to a trade-off between its preciseness and conciseness. Therefore, it is desirable to create DTD canditates with various degree of these two characteristics.

Generalization is based on replacing fragmets (sequences of subelements of a given element) from the input XML data by regular expressions, thus, using metacharacters like (*, +, ?). To provide a wide set of DTD canditates, each sequence is processed several times using various values of input parameters. Due to the very large number of possible DTD canditates, the authors employ certain real-life motivated heuristics.

For instance, the paper (\cite{Garofalakis:2000:XSE:342009.335409}) introduces the following example: Sequences \texttt{abab} and \texttt{bbbe} are generalized to \texttt{(ab)*}, \texttt{(a|b)*}, \texttt{b*e}.
\todo[inline]{Mozem takto pouzivat prevzate priklady?}

\subsection{Factoring}
Factoring is a process of creating a new DTD canditate from two or more DTD canditates, decresing their summed size without modifications in their semantics. An aim of this step is to decrease a MDL cost of DTD candidates calculated in the MDL step and thus refine the process of construction of the resulting DTD.

An example introduced it the paper (\cite{Garofalakis:2000:XSE:342009.335409}): DTD candidates \texttt{ac}, \texttt{ad}, \texttt{bc} and \texttt{bd} are factored into \texttt{(a|b)(c|d)}.

Alike the generalization step, also in this step the set of possible factored DTD is huge and the authors propose certain heuristics to make the factorization effective.

\subsection{Minimum Description Length (MDL) Principle}
This is an important step trying to create the resulting DTD with the best trade-off between its preciseness and conciseness.

Paper \cite{Mlynkova:2008:AAX:1494650.1495496} summarizes this step as follows: It expresses the quality of a DTD candidate using two aspects – conciseness and preciseness. Conciseness of a DTD is expressed using the number of bits required to describe the DTD (the smaller, the better). Preciseness of a DTD is expressed using the number of bits required for description of the input data using the DTD. In other words, the more accurately the structure is described, the fewer bits are required. Since the two conditions are contradictory, their balancing brings reasonable and realistic results.

\todo[inline]{Detailnejsie? Priklad?}

\todo[inline]{Popisat nejaky pristup vyuzivajuci ACO}

\section{SchemaMiner}
\todo[inline]{Popisat detailnejsie}
The SchemaMiner system \todo{bibref} is another example of a \emph{heuristic} \emph{merging state algorithm} creating the result in XSD. It focuses on inferring elements with the same name but different structure and unordered sequences.is another example of a \emph{heuristic} \emph{merging state algorithm} creating the result in XSD. It focuses on inferring elements with the same name but different structure and unordered sequences.
\todo[inline]{Definovat skratku XSD a co to je element type.}

@@

@@

\begin{enumerate}
\renewcommand{\theenumi}{(O\arabic{enumi})}
\renewcommand{\labelenumi}{\theenumi}
\item $L_1$ is a key of the elements $S_1$, $L_2$ is a respective foreign key and it itself is not a key of the elements $S_2$.
\item $L_2$ is a key of the elements $S_2$, $L_1$ is a respective foreign key and it cannot be decided whether $L_1$ is a key of the elements $S_1$ or not.
\end{enumerate}

@@

The pattern occurrence is considered of case (O1) if it is the for join pattern (weight: 1), if aggregation function \texttt{avg}, \texttt{min}, \texttt{max} or \texttt{sum} is applied on a return path (weight: 1) or if aggregation function \texttt{count} is applied on a return path (weight: 0.75). \todo {definovat return path?}
